Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-15 tensor/draft/draft-tensor-op.tex
[draft] correct subsection on posterior predictive

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.  The flat
term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed away from both \fred{Why
  both? At $q^2_{\rm max}$ it is strongly suppressed according to the formula
  given.} kinematic endpoints in $q^2$, except for $\ell = \tau$,
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  Non-zero values of
$A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}.

This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
non-vanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).

@@

We also perform a fit with non-zero $\wilson[NP]{9,\,10}$ \fred{Is this
  $\wilson[NP]{}$ ever introduced?} in order to assess the robustness of the
bounds with respect to interference. Note that $\wilson{7,7'}$ appears in linear
combinations with $\wilson{9,9'}$ such that its interference with tensor and
scalar couplings is captured implicitly by allowing new physics in
$\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
generality. In this case, $F_H^\mu$ by itself still provides bounds on
$|\wilson{T,\,T5}|$ that are weakened by a factor of two since $F_H^\mu$ does
not pose constraints on $\wilson{9,\,10}$ (in the chosen prior range). Once
additional experimental measurements of \reftab{tab:observables} are taken into
account, the potential destructive effects of new physics in $\wilson{9,\,10}$
become reduced and almost the same constraints on $\wilson{T,\,T5}$ are
recovered, as shown in the last column in \reftab{tab:cTT5:1-dimCLs}. If in
addition we allow $\wilson{S,S',P,P'} \ne 0$ (not shown in
\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%
which we attribute to cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
$F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the previous
bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by roughly 50\%.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{ The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ from
    only $F_H^\mu$~[grey dotted, left panel], only $\overline{\cal B}(B_s \to
    \bar\mu\mu)$ [blue dashed, center panel], and the combination with all other
    data in \reftab{tab:observables} as well as non-zero
    $\wilson[]{9,\,9',\,10,\, 10'}$ [red solid, right panel] at 68\% (darker)
    and 95\% (lighter) probability. The constraints on Re$(\wilson{P}Ê\pm
    \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$, apart from
    a small translation of the contours by $(+0.2,\, +0.15)$. The SM prediction is
    indicated by the black diamond. \checked{} }
  \label{fig:scalar}
\end{figure*}

@@

A non-redundant set of dimension-six operators of this effective theory (SM-EFT)
was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
order of the $W$-boson mass is presented in~\cite{D'Ambrosio:2002ex} for vector
couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows that SM
gauge groups in conjunction with the linear representation \todo{Ask Martin,
  Oscar how to correctly phrase this} impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm
  NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
$\Lambda_{\rm NP}$ is the high-energy scale at which new physics generates these
operators.

@@

\begin{figure*}
  \begin{center}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
    \end{center}
    \caption{ 68\% and 95\% contours of the 2D-marginalized distributions of
      scalar couplings $\wilson{S,\,S'}$ in the scenario SM-EFT with all
      constraints in \reftab{tab:observables} (red) when marginalising over
      non-zero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
      superimpose the corresponding contours from using only $\overline{\cal
        B}(B_s\to \bar\mu\mu)$ and all $B \to K \mu \bar{\mu}$ constraints
      (dashed blue contours) with fixed $\wilson[NP]{10,\,10'} = 0$.  The SM is
      indicated by the black diamond.  \checked{}}
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

It must be noted that the relations \refeq{eq:mEFT-constraints} are a
consequence of embedding the Higgs in a weak doublet along with the Goldstone
bosons.  For example choosing a non-linear representation of the scalar sector
allows additional dimension-six operators in the SM-EFT, such that the couplings
$\wilson{S,S',P,P'}$ are all independent and tensor operators have nonvanishing
couplings already at dimension six \cite{Cata:2015lta}.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  \begin{center}
  \begin{tabular}{cccccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $\quad T(5),\,9,\,10\quad$
  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-\todo{10}}$
  & $(0.2_{-1.1}^{+1.2}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & $(2.8_{-1.0}^{+1.6}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & $(1.6_{-1.2}^{+0.9}) \cdot 10^{-8}$
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
  \\
  \hline
  \multicolumn{2}{c}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
  & 1
  & SM
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
  \end{center}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not-yet-measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

Now we present the yet allowed ranges due to non-standard tensor and scalar
couplings of the so far unmeasured angular observables $J_{6c}$, $(J_{1s} - 3\,
J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$ in order to
explore the potential of their future measurements in fits of the kind pursued
in this work.  The 68\% probability intervals are collected in
\reftab{tab:postdictions} for the various model-independent scenarios, allowing
for interference with non-zero vector couplings, in \refsec{sec:tensor},
\refsec{sec:scalar} and \refsec{sec:tensor:scalar} for $q^2$-integrated
quantities in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and
$q^2\in [15,\, 19]$ GeV$^2$, respectively. Their posterior distributions have
been obtained from the posterior samples as explained in~\ref{app:mc}.

For comparison, the SM estimates are also given in \reftab{tab:postdictions}
multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
magnitude of vector couplings, note that for example the branching ratio of
$B\to K^*\bar\ell\ell$
\begin{align}
  \frac{{\rm d}\BR}{{\rm d}q^2} & = \frac{\tau_{B^0}}{3} \left[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
  \right]
\end{align}
is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
$q^2 \in [1,\, 6]$ and $[15,\, 19]$ GeV$^2$ bins.

The angular observable $J_{6c}$ is strictly zero in the absence of
tensor and scalar couplings. Non-zero contributions can be generated
in the SM by QED corrections or potentially from higher-dimensional
($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to
parametrical suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$,
respectively. Such a suppression must be compared to potential
suppression present for tensor and scalar contributions in particular
NP models in order to decide their relevance. Our model-independent
fits are still in a realm where such considerations are insignificant
since current experimental measurements, in combination with theory
uncertainties, do not impose yet too stringent constraints on tensor
and scalar couplings.

Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in
scenarios involving tensor couplings only and about ${\cal
  O}(10^{-10})$ in the presence of scalar couplings only. Both effects
are due to interference with vector couplings. Due to the strong
suppression of scalar couplings, the direct interference of scalar and
tensor contributions the allowed region in the most general scenario
\todo{schematic formula from notes}

Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
deviations from the SM prediction are possible only in the presence of non-zero
tensor couplings. In this case enhancement by two orders of magnitude are
possible up to the ${\cal O}(10^{-8})$ at high-$q^2$ and also at low-$q^2$ in
the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
experimental constraints in \reftab{tab:observables}. In view of current
experimental precision of $20\%$ of the branching ratio measurements at LHCb
\cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to the ${\cal
  O}(10^{-8})$, one can indeed hope for some sensitivity to such large effects
in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ for the not-yet-published 3
fb$^{-1}$ data set at least with the method of moments~\cite{beaujean:2015mom}.

The CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
non-vanishing width of the $B_s$ meson (cf. \refapp{app:BKstarellell})
can still take any value in the range $[-1,\, 1]$ in scenarios with
nonzero scalar couplings.

@@

We find that the experimental measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself constraints on tensor couplings $|\wilson{T,\,T5}|
  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|\wilson{T,\,T5}| < 0.33\,
  (0.43)$, even in the presence of non-standard contributions in vector
  couplings.
\item allows for the first time to bound all four scalar couplings $\wilson{i}$
  with $i = S,\,S',\,P,\,P'$ due to it's complementarity to $\overline{\cal B}(B_s
  \to \bar\mu\mu)$. Even when taking into account destructive interference with
  vector couplings, $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and
  $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%)
  probability. Currently, the bounds from $F_H^\mu$ are not as strong as those
  from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a factor four. In the
  future, measurements at LHCb and Belle II will further tighten the bounds.

>>>>

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.  The flat
term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed away from both \fred{Why
  both? At $q^2_{\rm max}$ it is strongly suppressed according to the formula
  given.} kinematic endpoints in $q^2$, except for $\ell = \tau$,
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  Nonzero values of
$A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}.

This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).

@@

We also perform a fit with nonzero $\wilson[NP]{9,\,10}$ \fred{Is this
  $\wilson[NP]{}$ ever introduced?} in order to assess the robustness of the
bounds with respect to interference. Note that $\wilson{7,7'}$ appears in linear
combinations with $\wilson{9,9'}$ such that its interference with tensor and
scalar couplings is captured implicitly by allowing new physics in
$\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
generality. In this case, $F_H^\mu$ by itself still provides bounds on
$|\wilson{T,\,T5}|$ that are weakened by a factor of two since $F_H^\mu$ does
not pose constraints on $\wilson{9,\,10}$ (in the chosen prior range). Once
additional experimental measurements of \reftab{tab:observables} are taken into
account, the potential destructive effects of new physics in $\wilson{9,\,10}$
become reduced and almost the same constraints on $\wilson{T,\,T5}$ are
recovered, as shown in the last column in \reftab{tab:cTT5:1-dimCLs}. If in
addition we allow $\wilson{S,S',P,P'} \ne 0$ (not shown in
\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%
which we attribute to cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
$F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the previous
bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by roughly 50\%.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{ The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ from
    only $F_H^\mu$~[grey dotted, left panel], only $\overline{\cal B}(B_s \to
    \bar\mu\mu)$ [blue dashed, center panel], and the combination with all other
    data in \reftab{tab:observables} as well as nonzero
    $\wilson[]{9,\,9',\,10,\, 10'}$ [red solid, right panel] at 68\% (darker)
    and 95\% (lighter) probability. The constraints on Re$(\wilson{P}Ê\pm
    \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$, apart from
    a small translation of the contours by $(+0.2,\, +0.15)$. The SM prediction is
    indicated by the black diamond. \checked{} }
  \label{fig:scalar}
\end{figure*}

@@

A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
order of the $W$-boson mass is presented in~\cite{D'Ambrosio:2002ex} for vector
couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows that SM
gauge groups in conjunction with the linear representation \todo{Ask Martin,
  Oscar how to correctly phrase this} impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm
  NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
$\Lambda_{\rm NP}$ is the high-energy scale at which new physics generates these
operators.

@@

\begin{figure*}
  \begin{center}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
    \end{center}
    \caption{ 68\% and 95\% contours of the 2D-marginalized distributions of
      scalar couplings $\wilson{S,\,S'}$ in the scenario SM-EFT with all
      constraints in \reftab{tab:observables} (red) when marginalising over
      nonzero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
      superimpose the corresponding contours from using only $\overline{\cal
        B}(B_s\to \bar\mu\mu)$ and all $B \to K \mu \bar{\mu}$ constraints
      (dashed blue contours) with fixed $\wilson[NP]{10,\,10'} = 0$.  The SM is
      indicated by the black diamond.  \checked{}}
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

It must be noted that the relations \refeq{eq:mEFT-constraints} are a
consequence of embedding the Higgs in a weak doublet along with the Goldstone
bosons.  For example choosing a nonlinear representation of the scalar sector
allows additional dimension-six operators in the SM-EFT, such that the couplings
$\wilson{S,S',P,P'}$ are all independent and tensor operators have nonvanishing
couplings already at dimension six \cite{Cata:2015lta}.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  \begin{center}
  \begin{tabular}{cccccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $\quad T(5),\,9,\,10\quad$
  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
  & $(0.2_{-1.1}^{+1.2}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & $(2.8_{-1.0}^{+1.6}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & $(1.6_{-1.2}^{+0.9}) \cdot 10^{-8}$
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
  \\
  \hline
  $A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$
  & --
  & 1
  & 1
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
  \end{center}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The posterior predictive 68\% probability intervals of not-yet-measured angular observables in
%     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new-physics scenarios given all the considered experimental
     constraints. The corresponding values for the SM (prior predictive) are given, too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for details. \checked{}
   }
\end{table*}

Now we discuss what the fits tells us about likely values of observables that
have not been measured yet but have sensitivity to tensor and scalar couplings.
In the $B\to K^*(\to K\pi)\bar\ell\ell$ decay, we again consider $(J_{1s} - 3\,
J_{2s})$ and $(J_{1c} + J_{2c})$ as in \refsec{sec:observables} and additionally
$J_{6c}$. We compute the posterior predictive distribution (see ~\ref{app:mc})
for each observable integrated over the low-$q^2$ bin $[1.1,\, 6]$~GeV$^2$ and
high-$q^2$ bin $[15,\, 19]$~GeV$^2$ matching LHCb's range. The distributions
resemble Gaussians, thus we summarize them by their modes and smallest 68\%
intervals in \reftab{tab:postdictions} comparing the SM (prior predictive,
$\wilson[NP]{i}=0$) to three NP scenarios. In each, we allow for interference
with the vector couplings and additionally vary only $\wilson{T,T5}$
(\refsec{sec:tensor}), only $\wilson{S^{(')},P^{(')}}$ (\refsec{sec:scalar}),
and finally both tensor and scalar couplings (\refsec{sec:tensor:scalar}).

We rescale the observables by the $B^0$-meson life time $\tau_{B^0} =
1.519$~ps~\cite{Agashe:2014kda} to be able to judge if experiments can measure
them in the near future.  At low $q^2$ the posterior predictive ranges are
${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, getting
suppressed down to ${\cal O}(10^{-10})$ at high $q^2$ due to the
$m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical magnitude
of vector couplings, note that for example the branching ratio of $B\to
K^*\bar\ell\ell$
\begin{align}
  \frac{{\rm d}\BR}{{\rm d}q^2} & = \frac{\tau_{B^0}}{3} \left[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
  \right]
\end{align}
is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
$q^2 \in [1,\, 6]$ and $[15,\, 19]$ GeV$^2$ bins.

The angular observable $J_{6c}$ is strictly zero in the absence of tensor and
scalar couplings. Nonzero contributions can be generated in the SM by QED
corrections or potentially from higher-dimensional ($d \geq 8$) $|\Delta B| =
|\Delta S| = 1$ operators, leading to parametric suppression by $\alpha_e/(4
\pi)$ or $(m_b/m_W)^2$. These factors should be compared to the potential
suppression present for tensor and scalar contributions in particular NP models
in order to gauge their relevance. Our model-independent fits are still in a
regime where such considerations are insignificant since current experimental
measurements, in combination with theory uncertainties, do not yet impose too
stringent constraints on tensor and scalar couplings.

Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in scenarios
involving tensor couplings only and about ${\cal O}(10^{-10})$ in the presence
of scalar couplings only. Both effects are due to interference with vector
couplings.  Schematically, $J_{6c}$ is a function of $\wilson{T} \times
\wilson{P} + \wilson{S} \times \wilson{T5}$, $\frac{m_{\ell}}{\sqrt{q^2}}
(\mbox{scalar}) \times (\mbox{vector})$, and $\frac{m_{\ell}}{\sqrt{q^2}}
(\mbox{tensor}) \times (\mbox{vector})$. The largest interval is obtained for
the scenario without scalar couplings because then the uncertainty on the
(tensor) couplings is largest. But even then, it seems the experimental
sensitivity will not be high enough to have an impact in global fits.

Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, substantial
deviations from the SM prediction are again only possible in the presence of
nonzero tensor couplings. In this case, an enhancement by two orders of
magnitude is possible up to ${\cal O}(10^{-8})$ at high $q^2$ and also at low
$q^2$ in the case of $(J_{1s} - 3\, J_{2s})$. We want to stress again that we
make these statements conditional on all included experimental constraints, the
scenario, and our prior. In view of the current experimental precision of $20\%$
on the branching ratio at LHCb \cite{Aaij:2013iag} with only 1 fb$^{-1}$,
corresponding to the ${\cal O}(10^{-8})$, one can indeed hope for some
sensitivity to such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\,
J_{2s})$ for the not-yet-published 3 fb$^{-1}$ data set. At least, we can hope
for some measurement if the method of moments~\cite{beaujean:2015mom} is
applied.

For the CP asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by the
nonvanishing width of the $B_s$ meson (cf. \refapp{app:BKstarellell}), we find a
rather uniform distribution in scenarios with nonzero scalar couplings. So any
value in the range $[-1,\, 1]$ is OK whereas we predict precisely one in the SM
and the scenario with only tensor couplings; cf.  the last row in
\reftab{tab:postdictions}. Hence any deviation from one would unambiguously hint
at the presence of scalar operators.

@@

We find that the experimental measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself constraints on tensor couplings $|\wilson{T,\,T5}|
  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|\wilson{T,\,T5}| < 0.33\,
  (0.43)$, even in the presence of nonstandard contributions in vector
  couplings.
\item allows for the first time to bound all four scalar couplings $\wilson{i}$
  with $i = S,\,S',\,P,\,P'$ due to it's complementarity to $\overline{\cal B}(B_s
  \to \bar\mu\mu)$. Even when taking into account destructive interference with
  vector couplings, $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and
  $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%)
  probability. Currently, the bounds from $F_H^\mu$ are not as strong as those
  from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a factor four. In the
  future, measurements at LHCb and Belle II will further tighten the bounds.
